### 2019-06-06 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Added leftbar to all defn,cor,thm etc

% Stochastic bandits were historically introduced as a simple model for clinical trials, where arms correspond to some treatments with unknown efficacy \cite{Thompson33}.
% More recently, MAB models have been proved useful for different applications, like cognitive radio, where arms can model the vacancy of radio channels, as presented in Chapter~\ref{chapter:4}, or parameters of a dynamically configurable radio hardware \cite{Maghsudi16,Bonnefoi17,KerkoucheAlami18}.
% Another application is the design of recommender systems, where arms model the popularity of different items (\eg, news recommendation, \cite{Li10}).
%
For both cognitive radio and recommender systems, the assumption that the arms distribution \emph{do not change over time} may be a big limitation. Indeed, in cognitive radio new devices can enter or leave the network, which impacts the availability of the radio channel they use to communicate; whereas in online recommendation, the popularity of items is also subject to trends. Hence, there has been some interest on how to take those \emph{non-stationary} aspects into account within a multi-armed bandit model.

@@

It could seem that the problem is considered as solved by this simple Exp3.S algorithm, but it was actively studied since the seminal paper \cite{Auer02NonStochastic}.
Two main reasons explain the dynamic research on this problem:
first, it is well known that despite their qualities, exponential-weights algorithms like Exp3 can usually be greatly outperformed by UCB-based algorithms, for stochastic problems, and so it is expected that Exp3.S can be outperformed by other algorithms, thus any practical application might benefit from algorithms more efficient than Exp3.S.
%
The second reason is that passively adaptive algorithms function as black-box models: they do not try to detect changes and do not explain why they changed from one arm to another. A lot of the recent research has been focussed on actively adaptive algorithms, precisely because they allow to interpret their decisions, by detecting changes on arms with statistical tests.
The piece-wise stationary MAB model was then studied by \cite{Kocsis06} and \cite{YuMannor09}.
%
This model is sometimes referred to as the abruptly changing \cite{WeiSrivastava18Abruptly}, or switching environments \cite{MellorShapiro13}.
%
In this model, described in full details in Section~\ref{sec:6:BanditSetting}, the (random) reward of arm $i$ at round $t$ has some mean $\mu_i(t)$, that is constant on intervals between two \emph{breakpoints}, and the regret is measured with respect to the \emph{current} best arm $i_t^* = \arg\max_{i} \mu_i(t)$.

@@

\paragraph{Outline.}
%
% This chapter is structured as follows.
We introduce the model and review related works in Section~\ref{sec:6:BanditSetting}. In Section~\ref{sec:6:ChangePointDetector}, we study the Generalized Likelihood Ratio test for sub-Bernoulli distributions (B-GLRT) as a Change-Point Detector (CPD) algorithm.
We introduce the two variants of \GLRklUCB{} algorithm in Section~\ref{sec:6:GLRklUCB_Algorithm}, where we also present upper bounds on the regret of both variants.
The unified regret analysis for these two algorithms is given in Section~\ref{sec:6:RegretAnalysis}.
Numerical experiments are presented in Section~\ref{sec:6:NumericalExperiments}, with more details in the Appendix.

@@

@@

A policy $\pi$ chooses the next arm to play based on the sequence of past plays and obtained rewards.
The performance of $\pi$ is measured by its (piece-wise stationary) \emph{regret}, the difference between the expected reward obtained by an oracle policy playing an optimal arm $i^*_t$ at time $t$, and that of the policy $\pi$,
%
\begin{equation}\label{def:6:nti}
    R_T^{\pi} = \E\left[\sum_{t=1}^T \left(\mu_{i^*_t}(t) - \mu_{I_t}(t)\right)\right].
\end{equation}

In the piece-wise \iid{} model, we furthermore assume that there is a (relatively small) number of \emph{breakpoints}, denoted by $\Upsilon_T:=\sum_{t=1}^{T-1} \indic\left(\exists i\in[K]: \mu_t(i) \neq \mu_{t+1}(i)\right)$.
If we denote $\tau^{(0)} = 0$, we define the $k$-th breakpoint recursively by
\begin{equation}
    \tau^{(k)} = \inf\{t > \tau^{(k-1)} : \exists i : \mu_i(t) \neq \mu_{i}(t+1)\}.
\end{equation}
%
Hence for $t\in[\tau^{(k)} + 1,\tau^{(k+1)}]$, that is on any stationary segments, the rewards $(X_{i,t})$ associated to each arm are \iid{} (hence the name of \emph{piece-wise stationary} problems).

@@

\begin{definition}[Sub-Bernoulli distributions]\label{def:6:subBernoulliDistributions}
    We call a \emph{sub-Bernoulli distribution} any distribution $\nu$ that satisfies
    $\ln \bE_{X\sim\nu}\left[e^{\lambda X}\right] \leq \phi_{\mu}(\lambda)$ with $\mu=\bE_{X\sim \nu}[X]$ and $\phi_{\mu}(\lambda) = \ln(1-\mu + \mu e^\lambda)$ is the log moment generating function of a Bernoulli distribution with mean $\mu$, for any $\mu\in[0,1]$.
\end{definition}

@@

\begin{definition}\label{def:6:GLRDef}
    The Bernoulli GLRT (B-GLRT) change point detector with threshold function $\beta(n,\delta)$ is the stopping time $\widehat{\tau}_{\delta}$ defined by
    %
    \begin{equation}\label{def:6:GLR}
        \widehat{\tau}_{\delta} := \inf \left\{ n \in \N^* : \sup_{s \in [2,n-1]} \left[s \times \kl\left(\widehat{\mu}_{1:s},\widehat{\mu}_{1:n}\right) + (n-s) \times \kl\left(\widehat{\mu}_{s+1:n},\widehat{\mu}_{1:n}\right)\right] \geq \beta(n,\delta)\right\}.
    \end{equation}
\end{definition}

@@

\begin{lemma}\label{lem:6:FalseAlarm}
    Let be $\bP_{\mu_0}$ a probabilistic model under which $X_t \in [0,1]$, and $X_t$ has an average of $\mu_0$ for all $t$.
    % Assume that there exists $\mu_0 \in [0,1]$ such that $\bE[X_t] = \mu_0$ and that $X_i \in [0,1]$ for all $i$.
    Then the B-GLRT test given in Definition~\ref{def:6:GLRDef} satisfies
    $\bP_{\mu_0}(\widehat{\tau}_\delta < \infty) \leq \delta$, with the threshold function
    %
    \begin{equation}\label{def:6:beta}
        \beta(n,\delta) = 2\cT\left(\frac{\ln(3n\sqrt{n}/\delta)}{2}\right) + 6\ln(1+\ln(n)).
    \end{equation}
\end{lemma}

@@

\begin{lemma}\label{lem:6:ConcFirst}
    $(X_i)_{i \in \N^*}$ and $(Y_i)_{i \in \N^*}$ two independent \iid{} processes with respective means $\mu$ and $\mu'$ such that
    $\bE[e^{\lambda X_1}] \leq e^{\phi_{\mu}(\lambda)}$ and $\bE[e^{\lambda Y_1}] \leq e^{\phi_{\mu'}(\lambda)}$,
    where $\phi_\mu(\lambda) = \bE_{X \sim \nu^{\mu}}[e^{\lambda X}]$ is the moment generating function of the distribution $\nu^\mu$, which is the unique distribution in an exponential family that has mean $\mu$.

    Let $\kl(\mu,\mu') = \KL(\nu^\mu,\nu^{\mu'})$ be the divergence function associated to that exponential family. Introducing the notation $\widehat{\mu}_s = \frac{1}{s}\sum\limits_{i=1}^s X_i$ and $\widehat{\mu}'_r = \frac{1}{r}\sum\limits_{i=1}^r Y_i$, it holds that for every $s,r \in \N^*$,
    \[\bP\left(\exists r \in \N^* : s \, \kl\left(\widehat{\mu}_{s},\mu\right) + r \, \kl\left(\widehat{\mu}_r',\mu'\right) > 3\ln(1+\ln(s)) + 3\ln(1+\ln(r)) + 2\cT\left(\frac{x}{2}\right)\right)\leq e^{-x},\]
    where $\cT$ is the function defined in \eqref{def:6:function_T}.
\end{lemma}
\begin{proof}
    This Lemma~\ref{lem:6:ConcFirst} is proved in Appendix~\ref{app:6:proofConcFirst}.
\end{proof}

@@

\begin{lemma}\label{lem:6:Delay}
    Let be $\bP_{\mu_0,\mu_1,\tau}$ a probabilistic model under which $X_t \in [0,1]$, and $X_t$ has an average of $\mu_0$ for all $t \leq \tau$, and $\mu_1$ for all $t > \tau$, with $\mu_0 \neq \mu_1$,
    and let $\Delta = |\mu_0 - \mu_1|$.
    Then the B-GLRT test given in Definition~\ref{def:6:GLRDef} satisfies
    \begin{equation}
        \bP_{\mu_0,\mu_1,\tau} (\widehat{\tau}_{\delta} \geq \tau + u) \leq \exp\left( -\frac{2\tau u}{\tau + u}\left(\max\left[ 0, \Delta - \sqrt{\frac{\tau + u}{2\tau u} \beta(\tau + u,\delta)} \right]\right)^2 \right).
    \end{equation}
\end{lemma}
%
\begin{proof}
    It is actually not used as such in the proofs of the regret upper bounds given below, because a similar but more specific result is used and proved in the proofs.
    For instance, see below in Section~\ref{par:6:controllingDelayInOneProof} in page~\pageref{par:6:controllingDelayInOneProof}.
    % \TODOL{We have to give the proof, or remove this result? Je ne vois pas le problème de le laisser là, ça formalise le résultat mais on a pas besoin de celui là, ça permet de bien formaliser ce qu'on entend par contrôler le délai, et dans la preuve plus bas on prouve ce qu'on souhaite.}
\end{proof}

@@

\begin{proposition}\label{prop:6:EnoughSamples}
    For every pair of instants $s \leq t\in\N^*$ between two restarts on arm $i$ (\ie, for a $k\in\{1,\dots,\NCi\}$, one has $\tau_i^{(k)} = \tau_i(t) < s \leq t < \tau_i^{(k+1)}$) it holds that
    \begin{equation}
        n_i(t) - n_i(s) \geq \left\lfloor \frac{\alpha}{K} (t-s) \right\rfloor.
    \end{equation}
\end{proposition}

@@

\begin{assumption}[Enough samples between two global change-points]
    \label{ass:6:LongPeriodsGlobal}
    Define
    \begin{equation}\label{def:6:DelayGlobal}
        d^{(k)} = d^{(k)}(\alpha,\delta) = \Bigl\lceil \frac{4K}{\alpha\left(\Delta^{(k)}\right)^2}\beta(T,\delta) + \frac{K}{\alpha} \Bigr\rceil.
    \end{equation}
    %
    Then \emph{we assume} that for all change $k \in \{1,\dots,\Upsilon_T\}$,
    $\tau^{(k)} - \tau^{(k-1)} \geq 2\max (d^{(k)},d^{(k-1)})$.
\end{assumption}

@@

\begin{theorem}\label{thm:6:mainRegretBoundGlobal}
    For $\alpha$ and $\delta$ for which Assumption~\ref{ass:6:LongPeriodsGlobal} is satisfied, the regret of \GLRklUCB{} with parameters $\alpha$ and $\delta$ based on \textbf{Global} Restart satisfies
    \begin{align}
        R_T \;\; \leq \;\; & 2\sum_{k=1}^{\Upsilon_T} \frac{4K}{\alpha \left(\Delta^{(k)}\right)^2}\beta(T,\delta) +\alpha T + \delta (K+1)\Upsilon_T \\
        & + \sum_{k=1}^{\Upsilon_T}\sum_{i : \mu_i^{(k)} \neq \mu_{k^*}^{(k)}} \frac{\left( \mu_{k^*}^{(k)}-\mu_i^{(k)}\right)}{\kl\left(\mu_i^{(k)},\mu_{k^*}^{(k)}\right)}\ln(T) + \bigO{\sqrt{\ln(T)}}. \nonumber
    \end{align}
\end{theorem}

@@

\begin{corollary}\label{cor:6:Global}
    For ``easy'' problems satisfying the corresponding Assumption~\ref{ass:6:LongPeriodsGlobal},
    let $\Delta^{\text{opt}}$ denote the smallest value of a sub-optimality gap on one of the stationary segments, and $\Delta^{\text{change}}$ be the smallest magnitude of any change point on any arm.
    \begin{enumerate}
        \item Choosing $\alpha = \sqrt{\frac{\ln(T)}{T}}$, $\delta = \frac{1}{\sqrt{T}}$ gives $R_T = \bigO{\frac{K}{\left(\Delta^{\text{change}}\right)^2} \Upsilon_T\sqrt{T\ln(T)} + \frac{(K-1)}{\Delta^{\text{opt}}} \Upsilon_T\ln(T)}$,
        \item Choosing $\alpha = \sqrt{\frac{\Upsilon_T\ln(T)}{T}}$, $\delta = \frac{1}{\sqrt{\Upsilon_T T}}$ gives $R_T = \bigO{\frac{K}{\left(\Delta^{\text{change}}\right)^2}\sqrt{\Upsilon_T T \ln(T)} + \frac{(K-1)}{\Delta^{\text{opt}}} \Upsilon_T\ln(T)}$.
    \end{enumerate}
\end{corollary}

@@

\begin{assumption}[Enough samples between two local change-points]
    \label{ass:6:LongPeriods}
    Define
    \begin{equation}\label{def:6:DelayLocal}
        d_i^{(\ell)} = d_i^{(\ell)}(\alpha,\delta) = \Bigl\lceil \frac{4K}{\alpha\left(\Delta_i^{(\ell)}\right)^2}\beta(T,\delta) + \frac{K}{\alpha} \Bigr\rceil.
    \end{equation}
    %
    Then \emph{we assume} that for all arm $i$ and all change-point of that arm $\ell \in \{1,\dots,\NCi\}$, $\tau_i^{(\ell)} - \tau_i^{(\ell-1)} \geq 2\max (d_i^{(\ell)},d_i^{(\ell-1)})$.
\end{assumption}

@@

\begin{theorem}\label{thm:6:mainRegretBound}
    For $\alpha$ and $\delta$ for which Assumption~\ref{ass:6:LongPeriods} is satisfied, the regret of \GLRklUCB{} with parameters $\alpha$ and $\delta$ based on Local Restart satisfies
    %
    \begin{equation}
        R_T \leq 2\sum_{i=1}^K\sum_{\ell=1}^{\NCi} \frac{4K}{\alpha \left(\Delta_i^{(\ell)}\right)^2}\beta(T,\delta) +\alpha T + 2 \delta \EffChange  + \sum_{i=1}^K\sum_{\ell=1}^{\NCi} \frac{\ln(T)}{\kl(\overline{\mu}_i^{(\ell)},{\mu}^*_{i,\ell})} +\bigO{\sqrt{\ln(T)}},
    \end{equation}
    where
    \begin{equation}
        {\mu}^*_{i,\ell} = \inf \left\{ \mu_{i_t^*}(t) : \mu_{i_t^*}(t) \neq \overline{\mu}_i^{(\ell)}, t \in [\tau_i^{(\ell)}+1, \tau_i^{(\ell+1)}]\right\}.
    \end{equation}
\end{theorem}

@@

\begin{lemma}\label{lem:6:GoodEventGlobal}
    With $\cE_T(\delta)$ defined as in \eqref{def:6:GoodEvenGlobal}, the ``bad event'' is unlikely:
    $\bP(\cE_T^c(\delta)) \leq \delta(K+1)\Upsilon_T$.
\end{lemma}

>>>>

% Stochastic bandits were historically introduced as a simple model for clinical trials, where arms correspond to some treatments with unknown efficacy \cite{Thompson33}.
% More recently, MAB models have been proved useful for different applications, like cognitive radio, where arms can model the vacancy of radio channels, as presented in Chapter~\ref{chapter:4}, or parameters of a dynamically configurable radio hardware \cite{Maghsudi16,Bonnefoi17,KerkoucheAlami18}.
% Another application is the design of recommender systems, where arms model the popularity of different items (\eg, news recommendation, \cite{Li10}).
%
For cognitive radio applications, as well as other applications such as recommender systems, the assumption that the arms distribution \emph{do not change over time} may be a big limitation.
Indeed, in cognitive radio, new devices can enter or leave the network, which impacts the availability of the radio channel they use to communicate.
And for instance in online recommendation, the popularity of items is also subject to trends.
Hence, there has been some interest on how to take those \emph{non-stationary} aspects into account within a multi-armed bandit model.

@@

It could seem that the problem is considered as solved by the Exp3.S algorithm, but it was actively studied since the seminal paper \cite{Auer02NonStochastic}.
Two main reasons explain the dynamic research on this problem:
first, it is well known that despite their qualities, exponential-weights algorithms like Exp3 can usually be greatly outperformed by UCB-based algorithms, for stochastic problems, and so it is expected that Exp3.S can be outperformed by other algorithms, thus any practical application might benefit from algorithms more efficient than Exp3.S.
%
The second reason is that passively adaptive algorithms function as black-box models: they do not try to detect changes and do not explain why they changed from one arm to another. A lot of the recent research has been focussed on actively adaptive algorithms, precisely because they allow to interpret their decisions, by detecting changes on arms with statistical tests.
The piece-wise stationary MAB model was then studied by \cite{Kocsis06} and \cite{YuMannor09}.
%
This model is sometimes referred to as the abruptly changing \cite{WeiSrivastava18Abruptly}, or switching environments \cite{MellorShapiro13}.
%
In this model, described in full details in Section~\ref{sec:6:BanditSetting}, the (random) reward of arm $i$ at round $t$ has some mean $\mu_i(t)$, that is constant on intervals between two \emph{breakpoints}, and the regret is measured with respect to the \emph{current} best arm $i_t^* = \arg\max_{i} \mu_i(t)$.

@@

\textbf{Outline.}
%
% This chapter is structured as follows.
We introduce the model and review related works in Section~\ref{sec:6:BanditSetting}. In Section~\ref{sec:6:ChangePointDetector}, we study the Generalized Likelihood Ratio test for sub-Bernoulli distributions (B-GLRT) as a Change-Point Detector (CPD) algorithm.
We introduce the two variants of \GLRklUCB{} algorithm in Section~\ref{sec:6:GLRklUCB_Algorithm}, where we also present upper bounds on the regret of both variants.
The unified regret analysis for these two algorithms is given in Section~\ref{sec:6:RegretAnalysis}.
Numerical experiments are presented in Section~\ref{sec:6:NumericalExperiments}, with more details in the Appendix.

@@

% \vfill{}

\textbf{Publications.}
%
This chapter is based on our articles \cite{Besson2019GLRT,Besson2019Gretsi}.

@@

A policy $\cA$ chooses the next arm to play based on the sequence of past plays and obtained rewards.
Like for stationary problems (see Definition~\ref{def:2:regret}), the performance of $\cA$ is measured by its (piece-wise stationary) \emph{regret}, the difference between the expected reward obtained by an oracle policy playing an optimal arm $i^*_t$ at time $t$, and that of the policy $\cA$
We use the same notation as the regret for stationary problem without ambiguity, as in this chapter we only consider the following definition.
%
\begin{equation}\label{def:6:nti}
    R_T^{\cA} = \E\left[\sum_{t=1}^T \left(\mu_{i^*_t}(t) - \mu_{I_t}(t)\right)\right].
\end{equation}

In the piece-wise \iid{} model, we furthermore assume that there is a (relatively small) number of \emph{breakpoints}, denoted by $\Upsilon_T:=\sum_{t=1}^{T-1} \indic\left(\exists i\in[K]: \mu_t(i) \neq \mu_{t+1}(i)\right)$.
If we denote $\tau^{(0)} = 0$, we define the $k$-th breakpoint recursively by
$\tau^{(k)} = \inf\{t > \tau^{(k-1)} : \exists i : \mu_i(t) \neq \mu_{i}(t+1)\}$.
%
Hence for $t\in[\tau^{(k)} + 1,\tau^{(k+1)}]$, that is on any stationary segments, the rewards $(X_{i,t})$ associated to each arm are \iid{} (hence the name of \emph{piece-wise stationary} problems).

@@

\begin{definition}[Sub-Bernoulli distributions]\label{def:6:subBernoulliDistributions}
\begin{leftbar}[defnbar]  % XXX leftbar defnbar, comment if needed
    We call a \emph{sub-Bernoulli distribution} any distribution $\nu$ that satisfies
    $\ln \bE_{X\sim\nu}\left[e^{\lambda X}\right] \leq \phi_{\mu}(\lambda)$ with $\mu=\bE_{X\sim \nu}[X]$ and $\phi_{\mu}(\lambda) = \ln(1-\mu + \mu e^\lambda)$ is the log moment generating function of a Bernoulli distribution with mean $\mu$, for any $\mu\in[0,1]$.
\end{leftbar}  % XXX leftbar defnbar, comment if needed
\end{definition}

@@

\begin{definition}\label{def:6:GLRDef}
\begin{leftbar}[defnbar]  % XXX leftbar defnbar, comment if needed
    The Bernoulli GLRT (B-GLRT) change point detector with threshold function $\beta(n,\delta)$ is the stopping time $\widehat{\tau}_{\delta}$ defined by
    %
    \begin{equation}\label{def:6:GLR}
        \widehat{\tau}_{\delta} := \inf \left\{ n \in \N^* : \sup_{s \in [2,n-1]} \left[s \times \kl\left(\widehat{\mu}_{1:s},\widehat{\mu}_{1:n}\right) + (n-s) \times \kl\left(\widehat{\mu}_{s+1:n},\widehat{\mu}_{1:n}\right)\right] \geq \beta(n,\delta)\right\}.
    \end{equation}
\end{leftbar}  % XXX leftbar defnbar, comment if needed
\end{definition}

@@

\begin{lemma}\label{lem:6:FalseAlarm}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    Let be $\bP_{\mu_0}$ a probabilistic model under which $X_t \in [0,1]$, and $X_t$ has an average of $\mu_0$ for all $t$.
    % Assume that there exists $\mu_0 \in [0,1]$ such that $\bE[X_t] = \mu_0$ and that $X_i \in [0,1]$ for all $i$.
    Then the B-GLRT test given in Definition~\ref{def:6:GLRDef} satisfies
    $\bP_{\mu_0}(\widehat{\tau}_\delta < \infty) \leq \delta$, with the threshold function
    %
    \begin{equation}\label{def:6:beta}
        \beta(n,\delta) = 2\cT\left(\frac{\ln(3n\sqrt{n}/\delta)}{2}\right) + 6\ln(1+\ln(n)).
    \end{equation}
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

@@

\begin{lemma}\label{lem:6:ConcFirst}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    $(X_i)_{i \in \N^*}$ and $(Y_i)_{i \in \N^*}$ two independent \iid{} processes with respective means $\mu$ and $\mu'$ such that
    $\bE[e^{\lambda X_1}] \leq e^{\phi_{\mu}(\lambda)}$ and $\bE[e^{\lambda Y_1}] \leq e^{\phi_{\mu'}(\lambda)}$,
    where $\phi_\mu(\lambda) = \bE_{X \sim \nu^{\mu}}[e^{\lambda X}]$ is the moment generating function of the distribution $\nu^\mu$, which is the unique distribution in an exponential family that has mean $\mu$.

    Let $\kl(\mu,\mu') = \KL(\nu^\mu,\nu^{\mu'})$ be the divergence function associated to that exponential family. Introducing the notation $\widehat{\mu}_s = \frac{1}{s}\sum\limits_{i=1}^s X_i$ and $\widehat{\mu}'_r = \frac{1}{r}\sum\limits_{i=1}^r Y_i$, it holds that for every $s,r \in \N^*$,
    \[\bP\left(\exists r \in \N^* : s \, \kl\left(\widehat{\mu}_{s},\mu\right) + r \, \kl\left(\widehat{\mu}_r',\mu'\right) > 3\ln(1+\ln(s)) + 3\ln(1+\ln(r)) + 2\cT\left(\frac{x}{2}\right)\right)\leq e^{-x},\]
    where $\cT$ is the function defined in \eqref{def:6:function_T}.
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}
\begin{proof}
    This Lemma~\ref{lem:6:ConcFirst} is proved in Appendix~\ref{app:6:proofConcFirst}.
\end{proof}

@@

\begin{lemma}\label{lem:6:Delay}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    Let be $\bP_{\mu_0,\mu_1,\tau}$ a probabilistic model under which $X_t \in [0,1]$, and $X_t$ has an average of $\mu_0$ for all $t \leq \tau$, and $\mu_1$ for all $t > \tau$, with $\mu_0 \neq \mu_1$,
    and let $\Delta = |\mu_0 - \mu_1|$.
    Then the B-GLRT test given in Definition~\ref{def:6:GLRDef} satisfies
    \begin{equation}
        \bP_{\mu_0,\mu_1,\tau} (\widehat{\tau}_{\delta} \geq \tau + u) \leq \exp\left( -\frac{2\tau u}{\tau + u}\left(\max\left[ 0, \Delta - \sqrt{\frac{\tau + u}{2\tau u} \beta(\tau + u,\delta)} \right]\right)^2 \right).
    \end{equation}
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}
%
\begin{proof}
    It is actually not used as such in the proofs of the regret upper bounds given below, because a similar but more specific result is used and proved in the proofs.
    For instance, see below in Section~\ref{par:6:controllingDelayInOneProof} in page~\pageref{par:6:controllingDelayInOneProof}.
    % \TODOL{We have to give the proof, or remove this result? Je ne vois pas le problème de le laisser là, ça formalise le résultat mais on a pas besoin de celui là, ça permet de bien formaliser ce qu'on entend par contrôler le délai, et dans la preuve plus bas on prouve ce qu'on souhaite.}
\end{proof}

@@

\begin{proposition}\label{prop:6:EnoughSamples}
\begin{leftbar}[propositionbar]  % XXX leftbar propositionbar, comment if needed
    For every pair of instants $s \leq t\in\N^*$ between two restarts on arm $i$ (\ie, for a $k\in\{1,\dots,\NCi\}$, one has $\tau_i^{(k)} = \tau_i(t) < s \leq t < \tau_i^{(k+1)}$) it holds that
    \begin{equation}
        n_i(t) - n_i(s) \geq \left\lfloor \frac{\alpha}{K} (t-s) \right\rfloor.
    \end{equation}
\end{leftbar}  % XXX leftbar propositionbar, comment if needed
\end{proposition}

@@

\begin{assumption}[Enough samples between two global change-points]\label{ass:6:LongPeriodsGlobal}
\begin{leftbar}[assumptionbar]  % XXX leftbar assumptionbar, comment if needed
    Define
    \begin{equation}\label{def:6:DelayGlobal}
        d^{(k)} = d^{(k)}(\alpha,\delta) = \Bigl\lceil \frac{4K}{\alpha\left(\Delta^{(k)}\right)^2}\beta(T,\delta) + \frac{K}{\alpha} \Bigr\rceil.
    \end{equation}
    %
    Then \emph{we assume} that for all change $k \in \{1,\dots,\Upsilon_T\}$,
    $\tau^{(k)} - \tau^{(k-1)} \geq 2\max (d^{(k)},d^{(k-1)})$.
\end{leftbar}  % XXX leftbar assumptionbar, comment if needed
\end{assumption}

@@

\begin{theorem}\label{thm:6:mainRegretBoundGlobal}
\begin{leftbar}[theorembar]  % XXX leftbar theorembar, comment if needed
    For $\alpha$ and $\delta$ for which Assumption~\ref{ass:6:LongPeriodsGlobal} is satisfied, the regret of \GLRklUCB{} with parameters $\alpha$ and $\delta$ based on \textbf{Global} Restart satisfies
    \begin{align}
        R_T \;\; \leq \;\; & 2\sum_{k=1}^{\Upsilon_T} \frac{4K}{\alpha \left(\Delta^{(k)}\right)^2}\beta(T,\delta) +\alpha T + \delta (K+1)\Upsilon_T \\
        & + \sum_{k=1}^{\Upsilon_T}\sum_{i : \mu_i^{(k)} \neq \mu_{k^*}^{(k)}} \frac{\left( \mu_{k^*}^{(k)}-\mu_i^{(k)}\right)}{\kl\left(\mu_i^{(k)},\mu_{k^*}^{(k)}\right)}\ln(T) + \bigO{\sqrt{\ln(T)}}. \nonumber
    \end{align}
\end{leftbar}  % XXX leftbar theorembar, comment if needed
\end{theorem}

@@

\begin{corollary}\label{cor:6:Global}
\begin{leftbar}[corollarybar]  % XXX leftbar corollarybar, comment if needed
    For ``easy'' problems satisfying the corresponding Assumption~\ref{ass:6:LongPeriodsGlobal},
    let $\Delta^{\text{opt}}$ denote the smallest value of a sub-optimality gap on one of the stationary segments, and $\Delta^{\text{change}}$ be the smallest magnitude of any change point on any arm.
    \begin{enumerate}
        \item Choosing $\alpha = \sqrt{\frac{\ln(T)}{T}}$, $\delta = \frac{1}{\sqrt{T}}$ gives $R_T = \bigO{\frac{K}{\left(\Delta^{\text{change}}\right)^2} \Upsilon_T\sqrt{T\ln(T)} + \frac{(K-1)}{\Delta^{\text{opt}}} \Upsilon_T\ln(T)}$,
        \item Choosing $\alpha = \sqrt{\frac{\Upsilon_T\ln(T)}{T}}$, $\delta = \frac{1}{\sqrt{\Upsilon_T T}}$ gives $R_T = \bigO{\frac{K}{\left(\Delta^{\text{change}}\right)^2}\sqrt{\Upsilon_T T \ln(T)} + \frac{(K-1)}{\Delta^{\text{opt}}} \Upsilon_T\ln(T)}$.
    \end{enumerate}
\end{leftbar}  % XXX leftbar corollarybar, comment if needed
\end{corollary}

@@

\begin{assumption}[Enough samples between two local change-points]\label{ass:6:LongPeriods}
\begin{leftbar}[assumptionbar]  % XXX leftbar assumptionbar, comment if needed
    Define
    \begin{equation}\label{def:6:DelayLocal}
        d_i^{(\ell)} = d_i^{(\ell)}(\alpha,\delta) = \Bigl\lceil \frac{4K}{\alpha\left(\Delta_i^{(\ell)}\right)^2}\beta(T,\delta) + \frac{K}{\alpha} \Bigr\rceil.
    \end{equation}
    %
    Then \emph{we assume} that for all arm $i$ and all change-point of that arm $\ell \in \{1,\dots,\NCi\}$, $\tau_i^{(\ell)} - \tau_i^{(\ell-1)} \geq 2\max (d_i^{(\ell)},d_i^{(\ell-1)})$.
\end{leftbar}  % XXX leftbar assumptionbar, comment if needed
\end{assumption}

@@

\begin{theorem}\label{thm:6:mainRegretBound}
\begin{leftbar}[theorembar]  % XXX leftbar theorembar, comment if needed
    For $\alpha$ and $\delta$ for which Assumption~\ref{ass:6:LongPeriods} is satisfied, the regret of \GLRklUCB{} with parameters $\alpha$ and $\delta$ based on Local Restart satisfies
    %
    \begin{equation}
        R_T \leq 2\sum_{i=1}^K\sum_{\ell=1}^{\NCi} \frac{4K}{\alpha \left(\Delta_i^{(\ell)}\right)^2}\beta(T,\delta) +\alpha T + 2 \delta \EffChange  + \sum_{i=1}^K\sum_{\ell=1}^{\NCi} \frac{\ln(T)}{\kl(\overline{\mu}_i^{(\ell)},{\mu}^*_{i,\ell})} +\bigO{\sqrt{\ln(T)}},
    \end{equation}
    where
    \begin{equation}
        {\mu}^*_{i,\ell} = \inf \left\{ \mu_{i_t^*}(t) : \mu_{i_t^*}(t) \neq \overline{\mu}_i^{(\ell)}, t \in [\tau_i^{(\ell)}+1, \tau_i^{(\ell+1)}]\right\}.
    \end{equation}
\end{leftbar}  % XXX leftbar theorembar, comment if needed
\end{theorem}

@@

\begin{lemma}\label{lem:6:GoodEventGlobal}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    With $\cE_T(\delta)$ defined as in \eqref{def:6:GoodEvenGlobal}, the ``bad event'' is unlikely:
    $\bP(\cE_T^c(\delta)) \leq \delta(K+1)\Upsilon_T$.
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}
